% Diogo Moreira personal CV
% I made this CV following this tutorial
% http://www.howtotex.com/general/a-guide-to-building-a-plain-and-simple-latex-cv/

\documentclass[a4paper,10pt]{article}
\usepackage{amsmath,amsfonts,amsthm} 
\usepackage[pdftex]{graphicx} 
\usepackage[utf8]{inputenc}
\usepackage[svgnames]{xcolor}
\usepackage{array, booktabs}
\usepackage{caption}
\usepackage{geometry}
\usepackage{multicol}
\geometry{
    a4paper,
    total={190mm,257mm},
    left=15mm,
    right=15mm,
    top=15mm,
    bottom=15mm
}
\usepackage{url}
\usepackage{hyperref}
\usepackage{sectsty}

\renewcommand\familydefault{\sfdefault}


\pagestyle{empty}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

\sectionfont{% 
	\sectionrule{0pt}{0pt}{-5pt}{0.25pt} 
}
	
\newlength{\spacebox} 
\settowidth{\spacebox}{88888888}
\newcommand{\sepspace}{\vspace*{0.75em}}

\newcommand{\Name}[1]{\noindent\huge\textbf{#1}\normalsize\normalfont}

\newcommand{\NewPart}[1]{\section*{\large{\textbf{#1}}}}

\newcommand{\PersonalEntry}[2]{
		\noindent\hangindent=0em\hangafter=0 		% Indentation
		\parbox{\spacebox}{							% Box to align text
		\textit{#1}}								% Entry name (birth, address, etc.)
		\hspace{4.5em} #2 \par}						% Entry value

\newcommand{\EducationEntry}[4]{
		\noindent \textbf{#1} \hfill 					% Study
		\colorbox{White}{%
			\parbox{6em}{%
			\hfill\color{Black}#2}} \par				% Duration
		\noindent \textit{#3} \par						% School
		\noindent \hangindent=0em\hangafter=0 \normalsize #4 	% Description
		\normalsize \par
		\vspace{0.5em}
	}

\newcommand{\WorkEntry}[4]{								% Same as \EducationEntry
		\noindent \textbf{#1} \hfill 					% Jobname
		\colorbox{White}{\color{Black}#2} \par			% Duration
		\noindent \textit{#3} \par						% Company
		\noindent\hangindent=2em\hangafter=0 \normalsize #4 	% Description
		\normalsize \par
		\vspace{0.5em}
	}
		
%%% ------------------------------------------------------------
%%% BEGIN DOCUMENT
%%% ------------------------------------------------------------
\begin{document}

\Name{Diogo Dantas Moreira}

%%% Personal details
%%% ------------------------------------------------------------


\begin{multicols}{2}

\PersonalEntry{email}{\texttt{\href{mailto:diogo.dmoreira@gmail.com}{diogo.dmoreira@gmail.com}}}
\PersonalEntry{phone/whatsapp}{+55 83 99655 1808}
\PersonalEntry{linkedIn}{\href{http://br.linkedin.com/in/diogodmoreira/}{/diogodmoreira}}
\PersonalEntry{github}{\href{http://github.com/diogomoreira}{/diogomoreira}}
\end{multicols}
%%% Education
%%% ------------------------------------------------------------

\NewPart{Professional experience}

\WorkEntry{Software Engineer}{Jun/2021 - Dec/2023}{\href{https://www.translucentcomputing.com/}{Translucent Computing}, Full-time}{Development of healthcare systems based on FHIR specs using Java with Spring Boot and Webflux/Reactive Web, NestJS (+Express) integrated with Kafka, Keycloak, Redis, PostgreSQL and Elasticsearch/Opensearch. Development of integration modules using OpenAI API. Development of a domain specific languages using Typescript and NodeJS APIs. Minor frontend tasks using React + Redux. I also worked on some tasks using Terraform, Shell Script and Kubernetes}

\WorkEntry{Adjunct Professor}{Oct/2014 - Present}{\href{https://www.ifpb.edu.br/}{Instituto Federal da Paraíba}, Full-time}{Lectures on Software Development / Software Engineering, covering topics such as Web Development (with HTML, CSS, Javascript, Node and Express), Software Testing (with JUnit + Mockito, Jest, Cypress and Selenium), Design Patterns, UML, REST, Spring Boot, Git, Maven and JavaEE.}

\WorkEntry{Software Engineer}{Jan/2013 - Oct/2014}{\href{http://www.phoebus.com.br/}{Phoebus Tecnologia}, Full-time}{Worked developing financial transaction processing backoffice systems using Java technologies with Spring Framework, Maven, JPA / Hibernate and Adobe Flex. Reports using Eclipse BIRT. Relational databases Oracle and Microsoft SQL Server. Systems documentation for IT Help Desk activities, such as deployment, update and version rollback.}

\WorkEntry{Software Developer}{Jun/2012-Jan/2013}{\href{https://www.indracompany.com/es/pais/brasil}{Indra Company}, Full-time}{Worked with development of Paraíba State Court of Justice systems using Java technologies, such as JSF 2.0 with Richfaces and Primefaces, JPA, Maven, HTML, CSS, XML.}

\WorkEntry{Developer}{Jan/2011-Jan/2012}{Recursive, Part-time}{The main assignment of the position was to develop a solution for a book library for a Federal Institute Campus. My assignments involved front-end and back-end development using Java technologies, such as EJB, JPA, JMS and Swing.}

\NewPart{Formal education/degree}

\EducationEntry{Master's in Software Engineering}{2017 - 2019}{\href{https://cesar.school/}{CESAR School} - Recife - PE, Brazil}{}

\EducationEntry{Specialization. MBA in Software Engineering}{2013 - 2014}{\href{https://estacio.br/}{Estácio iDEZ} - João Pessoa - PB, Brazil}{}

\EducationEntry{Undergraduate studies in Software Analysis and Development}{2008 - 2012}{\href{https://www.ifpb.edu.br/}{Instituto Federal da Paraíba} - Cajazeiras - PB, Brazil}{}


%%% Skills
%%% ------------------------------------------------------------

\NewPart{Skills}
\begin{multicols}{2}
\begin{itemize}
    \item \textbf{Backend}: Java 17, Spring Boot (Webflux/Reactive Web, Kafka, Data, Cloud), Java Server Faces, EJB, JMS. REST, GraphQL, NestJS, Node, Express.
    \item \textbf{Frontend}: HTML5, CSS (TailwindCSS, Sass, Styled Components, CSS Modules), JavaScript, TypeScript, React, Redux, Angular 2+, Static Site Generators (Gatsby and NextJS).
    \item \textbf{Testing}: JUnit, Mockito, Cucumber, Jest, Cypress, Selenium, JMeter, TestContainers.
    \item \textbf{Databases}: PostgreSQL (+PostGIS), MySQL, Oracle, Microsoft SQL Server, ImmuDB, MariaDB, ElasticSearch \& OpenSearch, Redis.
    \item \textbf{Tools}: Git, SVN, CVS. Jira. Docker, Jenkins, TravisCI. Keycloak. Kubernetes \& Helm. Shell Scripting. Basic understandment about Terraform.
\end{itemize}
\end{multicols}
% \vspace{-1cm}


% Languages and Frameworks
% \SkillsEntry{Software}{\textbf{Java}, JPA, Servlets, JSP, JSF, EJB}
% \SkillsEntry{}{Spring Framework, MVC \& Data}
% \SkillsEntry{}{HTML5 \& CSS}
% \SkillsEntry{}{Adoble Flex + ActionScript 3.0}
% \SkillsEntry{}{Projetos orientados a objeto utilizando UML}
% \SkillsEntry{}{Padrões de projeto orientado a objeto para aplicações desktop e web}
% \SkillsEntry{}{Android}
% \SkillsEntry{}{Shell Scripting}
% \SkillsEntry{}{Noções de desenvolvimento com C\# e ASP.NET MVC}

\sepspace

% Databases
% \SkillsEntry{Databases}{PostgreSQL (+PostGIS)}
% \SkillsEntry{}{Microsoft SQL Server}
% \SkillsEntry{}{Oracle Database}

\sepspace

% Tools

% \SkillsEntry{Ferramentas}{SCMs: CVS, SVN e GIT}
% \SkillsEntry{}{Maven}
% \SkillsEntry{}{Tomcat, Glassfish, Jetty Server}
% \SkillsEntry{}{JUDE / Astah}
% \SkillsEntry{}{SOAPUI}
% \SkillsEntry{}{Oracle SQL Developer}
% \SkillsEntry{}{Microsoft SQL Server Management}
% \SkillsEntry{}{Redmine}

% \NewPart{Idiomas}{}
% \SkillsEntry{}{Português (nativo)}
% \SkillsEntry{}{Inglês (avançado)}

%%% References
%%% ------------------------------------------------------------



\end{document}
